Git Learning Notes

### 2014-02-09 BackMatter/paper.tex
paper reading

@@

@@

>>>>

\citeauthor{Huang2006} studied the \ce{W3On} cluster with n from 7 to 10.\cite{Huang2006} It was found \ce{W3O9} clusters possess a HOMO-LUMO gap about 3.4eV. This closeness to bulk value suggests \ce{W3O9} could be viewed as the smallest molecular unit for bulk \ce{WO3}.

\ce{WO3} indirect gap 2.6eV, direct gap 3.4eV. \cite{Koffyberg1979}

Fingerprint of m-\ce{WO3}, h-\ce{WO3} and \ce{WO3,nH2O} were summarized in ref\cite{Daniel1987}.

 \ce{WO3} on FTO by flame synthesis.\cite{Rao2014} \cite{Xu2006}

 Seeded \ce{W_{18}O_{49}} NWs growth on W foil.\cite{Hong2006a}

 \ce{Na2W4O_{13}} growth and optical properties. \cite{Oishi2001} \cite{Itoh2001}

 For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH =0. \cite{Osterloh2008} flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.

\citeauthor{Salje1984} studied the transport in \ce{WO_{3-x}} ($0\leq x \leq 0.28$).\cite{Salje1984} It was found \ce{WO_{3-x}} show metallic conductivity when $x > 0.1$.

 \ce{WO3} high temperature phase. \cite{Vogt1999}

 tungsten bronzes \cite{Wiseman1976}

 Ge NW growth using Ga as catalyst. \cite{Chandrasekaran2006}

 Phase transformation of \ce{Na2MoO4} and \ce{Na2WO4} by Raman scattering. \cite{Lima2011}

 \ce{WO2} NWs synthesis and raman \cite{Ma2005}.

 \ce{WO_{3-x}} CS planes and conductivity.\cite{Sahle1983}

@@

\citeauthor{Hardcastle1990} summarized an empirical formula to relate the Raman peaks and \ce{Mo-O} bonding lengths.\cite{Hardcastle1990} This correlation assumes general form as
\begin{equation}\label{eq:mobond}
\nu = A \exp{B\cdot R},
\end{equation}
where $A=32895$ and $B=-2.073$ are fitting parameters, R is bond distance in unit of \AA. Given a stretching frequency, the resolution for calculated bond distance is $\pm0.016$\AA. The counterpart for \ce{W-O} bond \cite{Hardcastle1995} is 
\begin{equation}\label{eq:wobond}
\nu = 25823 \exp{-1.902\cdot R},
\end{equation}
with standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA. Another empirical expression connect the bond valence $s$ and bond distance R: $s(M-O) \approx (R/X)^{-6} $, where X=1.882 when M is Mo, and 1.904 when M is W. The valence sum rule could be then used to check the state of Mo cation. It should be noticed that not all observed Raman lines could be correlated to a \ce{Mo-O} bond distance by extrapolation of Eq.~\ref{eq:mobond}. It is then regarded as a symmetry related vibrational mode, i.e. $820 cm^{-1}$ in \ce{MoO3}. From the correlation of various Mo compounds, a general conclusion is the lower the stretching frequency for the shortest metal-oxygen bond, the more regular is the structure.

The observed raman lines of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm. The calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond} fit very well with the crystallographic value of \ce{Na5W_{14}O_{44}}. \cite{Triantafyllou1999a} The 107 peak probably arise from \ce{Na-O} bond.

The molecular unit in crystal exhibits different vibrational frequencies from that in solution or gas phases.

\ce{Na2Mo4O_{13}} phases monoclinic at RT, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. vapor pressure of \ce{Na2Mo4O_{13}} over \ce{MoO3}.

melting point of \ce{Na2Mo4O_{13}}
Mp: \ce{Na2Mo2O7} 960K

\ce{MoO3} vapor pressure:

The real phase diagram is the one between \ce{Na2Mo4O_{13}} and \ce{MoO3}.

the growth temperature could be much lower than the eutectic point.

KI MP:  681 
NaI MP: 661

NaOH Raman peaks lie at 3633 cm. \cite{walrafen2006} Raman scattering of \ce{Na2SiO3} exhibit major peak at 966 and 589 cm.\cite{Richet1996}

@@

multipeak Lorentzian fitting. 270 to 410 cm

In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.

Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs ( radial breathing modes) and G peaks position.\cite{Bonaccorso2013}

\citeauthor{Virsek2007} investigated the Raman scattering ($\lambda=632nm$) of \ce{WS2} NTs.\cite{Virsek2007} The silicon peak at 520 cm is used for calibration. Up-shift of A1g and E2g modes were observed, attributing to the strain in 3R stacking layers.

\citeauthor{Dobardzic2005} calculated \ce{MoS2} SWNT phonon dispersion. The dependence of wavenumbers and their displacement on chirality and diameter were discussed. The calculation method enable studying lattice dynamics with NT diameter up to 50nm. The chiral vector $(n_1, n_2)$ is defined within the Moly plane. Symmetry assignment is zigzag when $(n,0)$, armchair when $(n,n)$ and chiral when $(n_1, n_2), n_1>n_2$.

\begin{enumerate}
\item WS2 NT phase, 2H or 3R or 1T;

\end{enumerate}

\section{misc}

SOI:

VSS, growth kinetics,

### 2014-02-09 ch-moox/moox.tex
paper reading

\begin{table}[htb]
\centering
\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
\begin{tabular}{lcr}
\toprule
formula & structure  & remarks  \\
\midrule
\ce{A2O:MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
\ce{A2O:2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
\ce{A2O:3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
\ce{A2O:4MO3} & chain-type anions of \ce{MO6} & \\
\bottomrule

@@

\textbf{open questions}
\begin{itemize}
\item Is the liquid consumed? if so, how? : evaporation
\item How the size of liquid is related to the morphology evolution?
\item Possible doping level of alkaline ions
\item other lateral growth mode such as Ni-W-S system
\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
\item the interpretation of phase diagram
\item the overall molar amount of NaOH and MoO3 deposition
\item Young's parameters, contact angle informations, Gibbs free energy calculation
\item catalyst composition variation during growth
\end{itemize}

>>>>

\begin{table}[htb]
\centering
\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
\begin{tabular}{l1r}
\toprule
formula & structure  & remarks  \\
\midrule
\ce{A2O}:\ce{MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
\ce{A2O}:\ce{2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
\ce{A2O}:\ce{3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
\ce{A2O}:\ce{4MO3} & chain-type anions of \ce{MO6} & \\
\bottomrule

@@

\textbf{open questions}
\begin{itemize}
\item Is the liquid consumed? if so, how? : evaporation
\item How the size of liquid is related to the morphology evolution?
\item Possible doping level of alkaline ions
\item other lateral growth mode such as Ni-W-S system
\item VLS-VS interaction, or possible solution-liquid-solid, VSS,
\item the interpretation of phase diagram
\item the overall molar amount of NaOH and MoO3 deposition
\item Young's parameters, contact angle informations, Gibbs free energy calculation
\item catalyst composition variation during growth
\item \ce{Na2Mo4O_{13}} phases, solid solubility of \ce{Na2MoO4} in solid \ce{MoO3} is high. 
\item vapor pressure of \ce{Na2Mo4O_{13}} and \ce{MoO3}.
\end{itemize}

### 2014-02-09 ch-tms/tms.tex
paper reading

All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification or combination, as we shall discuss later. Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For precursor of \ce{WO3} NPs, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles. During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes. It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather a radical element under elevated temperature.

@@

@@

 \midrule
\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10nm Ni  & annealing under Ar for 1h at 850 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285nm \ce{SiO2}-Si, 500mg sulfur & 800 \si{\degreeCelsius} for 30 mins, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}. triangular flakes obtained\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\

\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}

>>>>

All these methods can be applied to the growth of TMDC few layer structures, either directly or with some modification or combination, as we shall discuss later. Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs are probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} has been thoroughly studied \cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For precursor of \ce{WO3} NPs, it was found that the simultaneous reduction and sulfurization is essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles. During the surfurization process, remaining oxide core is gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ CS planes. It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless introducing other reducing agents, such as \ce{H2}.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.

@@

\citeauthor{Zhang2013h} synthesized \ce{WS2} on sapphire using \ce{WO3} powder and sulfur as precursor under 900 C.  \cite{Zhang2013h} Ar slightly mixed with \ce{H2} is used to tailor the shape of \ce{WS2} flakes. \citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}/Si using \ce{WO3} powder and sulfur at 800 C, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL.\cite{Berkdemir2013} Raman excitation ($\lambda=532nm$)
It is worth noting that the growth conditions in Ref \cite{Peimyoo2013} and \cite{Zhang2013h} are basically identical except the usage of substrate. The flake size on sapphire seem larger than that on \ce{SiO2}/Si, either due to the nucleation barrier difference or the amount of growth vapor and growth time.

\cite{Song2013} ALD \ce{WS2}

@@

 \midrule
\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10nm Ni  & annealing under Ar for 1h at 850 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285nm \ce{SiO2}-Si, 500mg sulfur & 800 \si{\degreeCelsius} for 30 mins, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}. triangular flakes obtained\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Zhang2013h} & \ce{WO3} powders, sulfur (separate heating) & 900 \si{\degreeCelsius}, sapphire subs, 225mTorr, Ar 80 sccm and \ce{H2} 10 sccm, growth time 60mins, adjusting precursor and sapphire distance changing the coverage of \ce{WS2} \\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Peimyoo2013} & 1mg \ce{WO3} powders, sulfur,  & \ce{SiO2}/Si subs. Recipe A: 200mg S,RT-550, Sulfur begin to melt, 550-800, 5K/min, hold 10mins, 200 sccm Ar. Recipe B: sulfur separated heated at 250C\\
  & & \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}
